Experience shapes individual foraging specialization and success in a virtual predator-prey system

### 2023-10-17 manuscript/Chapter2-manuscript.Rmd
added more notes to par 2 and 3

Empirical studies on human and non-human hunters show that individuals optimize foraging efficiency (e.g. search and handling times, return rates) via associative images or reliance on prey and environmental cues [@Edwards.Jackson1994;@Morse2000;@MacDonald2007;@Reid.etal2010;@Wilson-Rankin2015]. Through this process, predators with extensive practice acquire expertise (e.g. skills, knowledge) that allows them to outperform novice hunters [@Dukas2019]. In light of this work, it has been suggested that experience may lead to individual foraging specialization (e.g. repeatedly using fast attacks) if a predator consistently increases its prey capture by using the same tactic through time [@Tinker.etal2009;@Dukas2019]. Yet, an alternative view is that learning operates as a mechanism driving behavioural flexibility. For instance, predators gain experience and information on their prey as they hunt in varying habitats, and may thus hunt optimally by adjusting their behaviour to the type of prey that they encounter [@Stephens1993;@Ishii.Shimada2010;@Mery.Burns2010;@Kelley.Magurran2011;@Snell-Rood2013]. To develop proper responses to fluctuating resources, individuals would need to sample their environment broadly during an extensive period, leading to greater performance at later stages of development [reviewed in @Snell-Rood2013]. The importance of context in defining how individual predators learn to hunt makes it difficult to predict whether they should specialize or not in their foraging behaviour with experience.

@@

Deux idées pour le paragraphe suivant :
1. Focus sur les contextes qui génèrent des différences, et qui devraient donc aussi mener à des différences de fitness (moins mettre l'accent sur le manque de consensus et plutôt focus sur les contextes, pour ensuite expliquer que donc ça devrait être mieux dans un que l'autre)
2. soit focus sur le fait qu'il y a des différences d'aptitude

>>>>

Empirical studies on human and non-human hunters show that individuals optimize foraging efficiency (e.g. search and handling times, return rates) via associative images or reliance on prey and environmental cues [@Edwards.Jackson1994;@Morse2000;@MacDonald2007;@Reid.etal2010;@Wilson-Rankin2015]. Through this process, predators with extensive practice acquire expertise (e.g. skills, knowledge) that allows them to outperform novice hunters [@Dukas2019]. In light of this work, it has been suggested that experience may lead to individual foraging specialization (e.g. repeatedly using fast attacks) if a predator consistently increases its prey capture by using the same tactic through time [@Tinker.etal2009;@Dukas2019]. Yet, an alternative view is that learning operates as a mechanism driving behavioural flexibility. For instance, predators gain experience and information on their prey as they hunt in varying habitats, and may thus hunt optimally by adjusting their behaviour to the type of prey that they encounter [@Stephens1993;@Ishii.Shimada2010;@Mery.Burns2010;@Kelley.Magurran2011;@Snell-Rood2013]. To develop proper responses to fluctuating resources, individuals would need to sample their environment broadly during an extensive period, leading to greater performance at later stages of development [reviewed in @Snell-Rood2013]. Context-dependence has proven to be key in defining how individual predators learn to hunt, making it challenging to predict under which circumstances they should specialize in their foraging with experience.

@@

Deux idées pour le paragraphe suivant :
1. Focus sur les contextes qui génèrent des différences, et qui devraient donc aussi mener à des différences de fitness (moins mettre l'accent sur le manque de consensus et plutôt focus sur les contextes, pour ensuite expliquer que donc ça devrait être mieux dans un que l'autre)
2. Je pourrais aussi commencer avec l'exemple indiquant que le foraging behaviour est lié aux proies rencontrées ou capturées
